---
title: "Milestone 4"
author: "Mike Silva"
date: "3/3/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(bookdown)
library(tinytex)
library(gt)
library(gtsummary)
library(stargazer)
library(knitr)


pdf_document2()
```

I am learning from Neil Schrage's code in his public repository in order to complete this milestone.^[this is an example of a footnote.I understand how to do this part, but I struggle with the overall setup of everything going on.]

I am replicating ["Assortative Mating on Ideology Could Operate Through Olfactory Cues"](https://onlinelibrary.wiley.com/doi/abs/10.1111/ajps.12133, by Rose McDermott, Dustin Tingley, and Peter K. Hatemi. This is a citation of the paper. @paper @paper1  

Here is an example of a table made using GT:

```{r gt, echo = FALSE}
x1 <- data.frame(a = sample(1:30, 10), b = sample(1:30, 10), c = sample(1:30, 10)) 
gt(x1) 
# kable(x = data.1, caption = "A Simple Table", position = "!h")
```


Here is an example of a regression table made using GT Summary:

```{r regression, echo=FALSE}
x2 <- data.frame(a = sample(1:30, 10), b = sample(1:30, 10), c = sample(1:30, 10))
fit_1 <- lm(x1$b ~ x2$a) 

table1 <- tbl_regression(fit_1) 
table1
```


Selected Bibliography + References: 
    
@paper1
